comgen-outline

### 2017-12-16 paper/case3-causals.Rmd
tweak causal figs

for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
 priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs <- webppl(l0.model, data = inputData, data_var = "data")
 cas.listener.predictions <- bind_rows(
   cas.listener.predictions, 
   l0.rs %>% select(Parameter,value) %>% mutate(distribution = p)
   )
}

>>>>

for (p in m.cas.fullmodel.prior.parameters.tidy$dist){
 priorParams <- m.cas.fullmodel.prior.parameters.tidy %>% filter(dist == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
  l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
 cas.listener.predictions <- bind_rows(
   cas.listener.predictions, 
      l0.rs.prior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Prior"),
    l0.rs.posterior %>% select(value) %>% mutate(distribution = p, Parameter = "state_Posterior")
   )
}
